---
title: 'The Truth is Revealed: Identity of the Fish Fry "Teti" Fishery in Eastern Cuba'
author:
  - Sheila Rodriguez-Machado:
      email: srodr62@lsu.edu
      institute: [UofO]
      correspondence: true
  - Tomas M. Rodriguez-Cabrera:
      email: tomasmichelrodriguez@gmail.com
      institute: [UofA]
      correspondence: false
institute:
  - UofO: Museum of Natural Sciences, Louisiana State University
  - UofA: Sociedad Cubana de Zoologia
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: '/Users/sheila_ffish/Documents/rrcompendium/analysis/templates/template.docx' # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: '/Users/sheila_ffish/Documents/rrcompendium/analysis/templates/journal-of-archaeological-science.csl' # Insert path for the bib-style
abstract: |
  texting texting
keywords: |
  amphidromy; Busck's Stone-Biting Goby; COI; Gobiidae 
   
editor_options: 
  chunk_output_type: console
---

<!-- This is the format for text comments that will be ignored during renderings. Do not put R code in these comments because it will not be ignored. -->

<!-- With the following code you can access and display values from the yml header above. -->

Keywords: `r rmarkdown::metadata$keywords`

<!-- The following code chunk defines some general settings how code chunks should behave. -->

```{r setup, echo = FALSE}    
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/",
  dpi = 300
)

#knitr::opts_knit$set(root.dir = '../rrcompendium/')

#getwd()

```


```{r}

# INSTALLING PACKAGES AND LIBRARIES - if needed
packages = c("raster", "ggplot2", "ggthemes",  
             "rentrez", "ape", "seqinr", "msa", "Biostrings", "systemPipeR", "phangorn", "ggtree")

package.check <- lapply(packages, FUN = function(x) {
    if (!require(x, character.only = TRUE)) {
      install.packages(x, dependencies = TRUE)
      library(x, character.only = TRUE, include = FALSE, warn.conflicts = FALSE, quietly = TRUE)
    }
  }
)

```

<!-- The actual document text starts here: -->

# Introduction

Here is a citation [@Marwick2017]

# Methods

Tetis (19–28 mm standard length) were collected 400 m from the river mouth of Río Yumurí (Figure 2.1), eastern Cuba, in December, 2018. Samples were collected using hand nets (1 mm mesh size) 2 m from the riverbank. Specimens were anesthetized using MS 222 (Tricaine Methanesulphonate) and immediately preserved in 80% ethanol. Voucher specimens were deposited in the collection of the Acuario Nacional de Cuba (catalog number: ANC-xxxx).

```{r mainMap, fig.cap="Sampling site at Yumuri river mouth, Eastern Cuba"}

# getting the map of Cuba
mydata <- getData("GADM", country = "cuba", level = 1)  # package raster
mymap <- fortify(mydata)                                # package ggplot2

# sampling site
dots <- data.frame(
  long = c(-74.293460),
  lat = c(20.298537),
  names = c("Yumuri river mouth"),
  stringsAsFactors = FALSE
  ) 

# main map
mainMap <-  ggplot() +
       geom_blank(data = mymap, aes(x = long, y = lat)) +
       geom_map(data = mymap, map = mymap, aes(group = group, map_id = id), fill = "gray90", color = "black", size = 0.3) +
       scale_x_continuous(limits = c(-74.51, -74.11), expand = c(0, 0)) +
       scale_y_continuous(limits = c(20.13, 20.42), expand = c(0, 0)) +
       geom_point(data = dots, aes(x = long, y = lat), color = "red", size = 4) +     
       coord_equal() +
       theme_bw()

# small square framing the zomm area
zoomOut <- data.frame(long = c(-74.49, -74.49, -74.09, -74.09, -74.49),
                   lat = c(20.13, 20.40, 20.40, 20.13, 20.13))

# inset map
insetMap <- ggplotGrob(
      ggplot() +
      geom_blank(data = mymap, aes(x = long, y = lat)) +
      geom_map(data = mymap, map = mymap, aes(group = group, map_id = id), fill = "gray95", color = "black", size = 0.3) +
      geom_path(data = zoomOut, aes(x = long, y = lat), size = 0.3) +
      scale_x_continuous(limits = c(-85.47, -73.65), expand = c(0, 0)) +
      scale_y_continuous(limits = c(19.5, 23.5), expand = c(0, 0)) +
      coord_map("polyconic") +
      theme_map() +     # package ggthemes
      theme(panel.background = element_rect(fill = NULL)) # fill = NULL or transparent, with color=NA both the background and the frame are transparent
      )

mainMap +
      annotation_custom(grob = insetMap, xmin = -74.12, xmax = -74.37,
                        ymin = 20.31, ymax = 20.42)


```

Total DNA was extracted from caudal peduncle muscle tissues using the DNAeasy tissue kit (QIAGEN). Partial sequences of the mitochondrial gene cytochrome oxidase I (COI) were amplified through the polymerase chain reaction in 20 μL of reaction volume (one unit of GoTaq DNA polymerase-Promega, 0.2 nM of each primer, 0.2 μM dNTPs, and 1.5 mM MgCl2) [@lara2010dna]. We used the primers COIf (5´-AAYCAYAAAGAYGGYACCCT-3´) and COIr (3´-CCTCNGGRTGNCCRAAGAAYCA-5´) [@palumbi1991simple].  

PCR products were purified using ExoSAP-IT™ PCR Product Cleanup Reagent (Affymetrix Inc./ USB, Cleveland, OH, USA), and then sequenced on an ABI 3100 automated sequencer (Applied Biosystems). Raw sequence files were edited and aligned with the software Geneious v.9.1 [@kearse2012geneious], and submitted to GenBank database (accession numbers #####). We used sequences of the genus *Sicydium* as reference for recovering the taxonomic identity of the "tetis". Sequences of *Awaous banana* and *A. ocellaris* were used as outgroup. All non-Cuban sequences were recovered from GenBank using the R package *rentrez* [@winter2017rentrez]. Duplicated sequences and sequences with missing data were excluded. Sequences were edited using the R packages *seqinr* [@charif2007seqinr], *ape* [@paradis2015package], and *biostrings* [@pages2013package]. Final alignment was obtained with the algorithm ClustalOmega (@sievers2011fast) using the R package *msa* [@bodenhofer2015msa].

```{r gettingAPI}

                                                            # DOWNLOADING SEQS FROM GENBANK
# rentrez: this package provides an R interface NCBI API and allows to search databases like GenBank (http://www.ncbi.nih.gov/genbank/) 

Sicydium_COI <- "Sicydium[Organism] AND COI[Gene]"

# I set retmax=580 because after running this by default, I got a message with the number of hits (580 in this case)
Sicydium_COI_search <- entrez_search(db = "nuccore", term = Sicydium_COI, retmax = 580)

# given that the search is too big for the system, it needs to be split into two smaller ones
Sicydium_COI_seqs1 <- entrez_fetch(db = "nuccore", id = Sicydium_COI_search$ids[0:295], rettype = "fasta")
Sicydium_COI_seqs2 <- entrez_fetch(db = "nuccore", id = Sicydium_COI_search$ids[296:580], rettype = "fasta")

# GETTING OUTGROUP SEQUENCES OF AWAOUS BANANA (2) AND A. OCELLARIS (2)

Awaous_bananaCOI <- "Awaous_banana[Organism] AND COI[Gene]"
Awaous_bananaCOI_search <- entrez_search(db = "nuccore", term = Awaous_bananaCOI, retmax = 2)
Awaous_bananaCOI_seqs <- entrez_fetch(db = "nuccore", id = Awaous_bananaCOI_search$ids, rettype = "fasta")

Awaous_ocellarisCOI <- "Awaous_ocellaris[Organism] AND COI[Gene]"
Awaous_ocellarisCOI_search <- entrez_search(db = "nuccore", term = Awaous_ocellarisCOI, retmax = 4)
Awaous_ocellarisCOI_seqs <- entrez_fetch(db = "nuccore", id = Awaous_ocellarisCOI_search$ids, rettype = "fasta")

# storing ALL sequences in a single fasta file
write(Sicydium_COI_seqs1, file="../rrcompendium/analysis/data/raw_data/Sicydium_COI_1-seqs.fasta", sep = "\n")
write(Sicydium_COI_seqs2, file="../rrcompendium/analysis/data/raw_data/Sicydium_COI_1-seqs.fasta", sep = "\n", append = TRUE)   # 'append = TRUE', I can keep adding seqs
write(Awaous_bananaCOI_seqs, file="../rrcompendium/analysis/data/raw_data/Sicydium_COI_1-seqs.fasta", sep = "\n", append = TRUE)
write(Awaous_ocellarisCOI_seqs, file="../rrcompendium/analysis/data/raw_data/Sicydium_COI_1-seqs.fasta", sep = "\n", append = TRUE)


```

```{r editingAPI}

# seqinr: package for sequence manipulation 
# reading the file and renaming the sequences

Sicydium_COI_seqinrFormat <- read.fasta(file ="../rrcompendium/analysis/data/raw_data/Sicydium_COI_1-seqs.fasta", seqtype = "DNA", as.string = TRUE, forceDNAtolower = FALSE)

Sicydium_COI_names <- attr(Sicydium_COI_seqinrFormat, "name")      # editing species name
Sicydium_COI_names <- gsub("\\..*", "", Sicydium_COI_names)        # eliminating characters after "." using gsub
Sicydium_COI_names <- gsub("^.*\\|", "", Sicydium_COI_names)       # eliminating characters before "|" using gsub

# using library "ape"
Sicydium_COI_apeFormat <- read.GenBank(Sicydium_COI_names)         # this line takes a few minutes to run

# creating a vector (to be added as name of the seqs) with the species, GenBank accession number, and type of gene
Sicydium_COI_GenBank_Ids <- paste(attr(Sicydium_COI_apeFormat, "species"), names(Sicydium_COI_apeFormat), sep = "_COI_")

# writing a new fasta file (2nd) using the vector above 
write.fasta(sequences = Sicydium_COI_seqinrFormat, names = Sicydium_COI_GenBank_Ids, nbchar = 10,
            file.out = "../rrcompendium/analysis/data/raw_data/Sicydium_COI_2-seqinrFormat.fasta")


                                     # EDITTING SEQS AND GETTING THEM ALL READY FOR THE PHYLOGENETIC ANALYSIS

### REMOVING sequences of incomplete/unspecific NAMES; that is, those with 'sp.'
nameFasta <- read.fasta(file = "../rrcompendium/analysis/data/raw_data/Sicydium_COI_2-seqinrFormat.fasta",
                        seqtype = "DNA", as.string = TRUE, forceDNAtolower = FALSE)

fastaNames <- strsplit(names(nameFasta), '_')                  # creating a vector splitting species names
completeSeqs <- which(! grepl("sp.", fastaNames))              # selecting only those with specific name in them  

# writing a new fasta (3rd) file with only those seqs with full scientific names
write.fasta(sequences = nameFasta[completeSeqs], names = names(nameFasta)[completeSeqs],
            file.out = "../rrcompendium/analysis/data/raw_data/Sicydium_COI_3-names.fasta")

### REMOVING sequences of LENGTH shorter than 600 pb, given that the gene COI has between 627 and 658 bp.
lengthFasta <- read.fasta(file = "../rrcompendium/analysis/data/raw_data/Sicydium_COI_3-names.fasta",
                          seqtype = "DNA", as.string = TRUE, forceDNAtolower = FALSE)                     # 586 seqs
fastaLength <- lengthFasta[which(getLength(lengthFasta) >= 600)]
write.fasta(sequences = fastaLength, names = names(fastaLength),
            file.out = "../rrcompendium/analysis/data/raw_data/Sicydium_COI_4-lengths.fasta")             # 401 seqs

### Removing DUPLICATE sequences
# using "seqinr" to do it 
# for not using attributes to name sequences
duplicatesFasta <- read.fasta("../rrcompendium/analysis/data/raw_data/Sicydium_COI_4-lengths.fasta", set.attributes = FALSE) 

seqnames <- names(duplicatesFasta)
dups <- grep(TRUE,duplicated(duplicatesFasta))
uniqueNames <- seqnames[-dups]
uniqueSeqs <- duplicatesFasta[-dups] 
write.fasta(sequences = uniqueSeqs, names = uniqueNames,
            file.out = "../rrcompendium/analysis/data/raw_data/Sicydium_COI_5-dupli.fasta")               # 204 seqs

# adding samples from Cuba (n=6)
mySamples <- read.fasta("../rrcompendium/analysis/data/raw_data/Sicydium_COI_Cuba.fas")
write.fasta(mySamples, names(mySamples),
            "../rrcompendium/analysis/data/raw_data/Sicydium_COI_5-dupli.fasta", open = "a")              # 210 seqs


```

```{r alignment}
invisible({capture.output({                ### ALIGNING the sequences        # libraries "msa" and "Biostrings"

alignmentFasta <- readDNAStringSet("../rrcompendium/analysis/data/raw_data/Sicydium_COI_5-dupli.fasta")
ClustalOAlignment <- msa(alignmentFasta, "ClustalOmega")
# print(ClustalOAlignment, showConsensus=FALSE, showNames=TRUE, show="complete") 

# Checking for the position of sequences that were not edited properly so they still have nucleotides different that A, G, C, T 
nucType <- alphabetFrequency(ClustalOAlignment)
unknownNuc <- nucType[, c(5:14)]
unknownPosition <- which(unknownNuc > 0, arr.ind=T)

# REMOVING samples with too many GAPS at the beginning and the end of the sequences and UNKNOWN nucleotides (ex.: W, K, S) 
colmask(ClustalOAlignment) <- IRanges(start=c(1,666),end=c(25,679))
rowmask(ClustalOAlignment) <- IRanges(start=c(1),end=c(1))
ClustalOAlignment2 <- as(ClustalOAlignment, "DNAStringSet")
writeXStringSet(ClustalOAlignment2,
                file="../rrcompendium/analysis/data/raw_data/Sicydium_COI_6-alignment.fasta")           # 209 seqs -- 640 bp

### Replacing gaps at the begining and end with Ns
gapsFasta <- read.fasta(file = "../rrcompendium/analysis/data/raw_data/Sicydium_COI_6-alignment.fasta", seqtype = "DNA", as.string = TRUE, forceDNAtolower = FALSE, apply.mask = FALSE)
#getLength(gapsFasta)
replacingGaps <- lapply(gapsFasta, function(x) gsub("-", "N", x))
write.fasta(replacingGaps, names(replacingGaps), "../rrcompendium/analysis/data/raw_data/Sicydium_COI_7-gaps.fasta")

})})

```


```{r warning = FALSE}
invisible({capture.output({               ### GETTING the READING FRAME     --- library "systemPipeR"
                                          
alignedFasta <- readDNAStringSet("../rrcompendium/analysis/data/raw_data/Sicydium_COI_7-gaps.fasta") 

getRF <- function(alignedFasta){
  if (class(alignedFasta)!= c("DNAStringSet")){
    stop("This function only takes files of class 'DNAStringSet'. Use package 'Biostrings' to read the input file")
  }
  if (any(letterFrequency(alignedFasta, "-", as.prob=TRUE))>0){
    stop("This function do not take gaps as values/strings. Go and replaced gaps with Ns (if the gaps are at the begining or end of the sequences) or choose a subset of sequences that do not contain gaps")
  }
  orf1 <- predORF(alignedFasta[1:10], n=1, type="df", mode="orf", strand="sense")   # predORF() do not read seqs with gaps
  # predicts longest ORF for sense strand in each query sequence                                                                          
  longestSeq1 <- orf1$start[orf1$width == max(orf1$width)]
  codonPosition1 <- longestSeq1[1]/3
  codonConfirmation1 <- round(codonPosition1)
  if (codonPosition1==codonConfirmation1){
   file.rename("../rrcompendium/analysis/data/raw_data/Sicydium_COI_7-gaps.fasta", "../rrcompendium/analysis/data/raw_data/Sicydium_COI_newRF.fasta")                     # 640 bp
  print("The Reading Frame of these seqs is +1, no further action is required, go to modelTesting")
    } else {
    if (codonPosition1!=codonConfirmation1){
      tempLength <- length(alignedFasta[[1]])
      #remove first nucleotide position
      newRF2 <- subseq(alignedFasta, start = 2, end = tempLength)      # 639 bp
      # getting new RF from the new alignment with -1 bp.
      orf2 <- predORF(newRF2[1:10], n=1, type="df", mode="orf", strand="sense") 
      # checking size gain
      longestSeq2 <- orf2$start[orf2$width == max(orf2$width)]
      codonPosition2 <- (longestSeq2[1]+2)/3
      codonConfirmation2 <- round(codonPosition2)
      if (codonPosition2==codonConfirmation2){
        writeXStringSet(newRF2, file="../rrcompendium/analysis/data/raw_data/Sicydium_COI_newRF.fasta")
      print("The Reading Frame of these seqs was +2, new fasta file created, go to modelTesting")
      } else {
      if (codonPosition2!=codonConfirmation2){
        #remove first nucleotide position
        tempLength <- length(alignedFasta[[1]])
        newRF3 <- subseq(alignedFasta, start = 3, end = tempLength)
        writeXStringSet(newRF3, file="../rrcompendium/analysis/data/raw_data/Sicydium_COI_newRF.fasta")    # 638 bp
      print("The Reading Frame of these seqs was +3, new fasta file created, go to modelTesting")
     }
   }  
  }
 }
}


suppressWarnings(suppressMessages(print(getRF(alignedFasta))))

})})


```

The nucleotide substitution model that best explained our data was estimated using the function modelTest from the R package phangorn [@schliep2011phangorn]. The phylogenetic tree was reconstructed following a maximum mikelihood approach [@felsenstein1981evolutionary] using the functions optim.pml and bootstrap.pml, also from the package phangorn. The tree was generated and visualized using the R package ggtree [@yu2017ggtree].

```{r bestModel, warning = FALSE}
                                      # FINDING THE BEST NUCLEOTIDE SUSBSTITUTION MODEL

# libraries ape and phangorn (modelTest is a function of the package phangorn)

fastaRF <- read.dna(file="../rrcompendium/analysis/data/raw_data/Sicydium_COI_newRF.fasta", format = "fasta")

fastaRF1 <- read.fasta(file = "../rrcompendium/analysis/data/raw_data/Sicydium_COI_6-alignment.fasta", seqtype = "DNA", as.string = TRUE, forceDNAtolower = FALSE, apply.mask = FALSE)
getLength(fastaRF1)

getBestModel <- function(fastaRF){
  if (class(fastaRF)!= c("DNAbin")){
    stop("This function only takes files of class 'DNAbin'. Use package 'ape' to read the input file")
  }
  formatPhyDat <- as.phyDat(fastaRF)                #getting the class used by modelTest: phyDat or pml
  modelChoice <- modelTest(formatPhyDat, tree = NULL, model = c("JC", "K80", "HKY", "TrN", "SYM", "GTR"), multicore = TRUE, mc.cores = 4)
  modelChoiceSorted <- as.data.frame(modelChoice[order(modelChoice$AICc),])
  return(modelChoiceSorted)
}
  
bestModel <- suppressWarnings(suppressMessages(getBestModel(fastaRF)))               # getting the AICc for each competing model

# DISCLAIMER: visually inspecting the AICc is better than just getting the best model automatically, because it allows to compares models with similar AICc and it is my personal opinion to choose the one with the least parameters.  
# The alternative is to get automatically the first model that the data.frame modelTest gives and storing it as a variable. In order to get this as reproducible as possible, I chose the alternative.


```

```{r tree, include=TRUE, results = 'hide', fig.show='hide'}

                                                        # BUILINDG THE TREE
# --- library: phangorn
env = attr(bestModel, "env")    # getting the AICc for each competing model sorted
fitStart = eval(get(bestModel$Model[which.min(bestModel$AICc)], env), env)    # initial fit for the model chosen

# avoid to create a tree every time the code runs
#set.seed(2015-07-01)

fit = optim.pml(fitStart, rearrangement = "stochastic", optGamma=TRUE, optInv=FALSE, model="HKY")     # seeking a maximum likelihood solution
set.seed(123)    # getting the same tree topology each time the code runs 
bs = bootstrap.pml(fit, bs=100, optNni=TRUE, multicore=TRUE, mc.cores = 4)

# saving the tree in the folder 'analysis/figures/'
bsTree <- plotBS(midpoint(fit$tree), bs, p = 75, type="p", bs.col = "blue")     # fit$tree is where the optimal tree is stored
optimalTree <- plotBS(bsTree, type = "p", cex = 0.2, font = 1)
# export tree with bootstrap values as node labels
write.tree(optimalTree, file="../rrcompendium/analysis/data/derived_data/Sicydium_ML_tree.tre")                     


```

# Results

hshdhdhdh

```{r demo-plot1, fig.cap="A plot of random numbers"}
plot(rnorm(10))
```


```{r inline-code2, include = TRUE, results='hide'}
# the result wont be displayed in the final document
loglikelihood <- round(-1*(as.numeric(fit[1])), 2)

```

```{r Sicydium_ML_tree, fig.cap = paste("ML phylogenetic tree  (-lnL =", loglikelihood,") depicting the relationships among all available COI sequences of the genus *Sicydium*. Sequences highlited in green represent samples from Cuba. Numbers on branches represent boostrap values higher than 70.")}

# , fig.width = 11.8, fig.height = 10

# Editing and visualizing the tree to represent --- library: ggtree
tree <- read.tree(file="../rrcompendium/analysis/data/derived_data/Sicydium_ML_tree.tre")

# checkinf whether the tree is rooted
rootedTree <- is.rooted(tree)   # package ape. showing the tree root: geom_rootpoint(color="pink", size=5) 

# getting the node number for each main clade. This info is important because those #s are the one needed to edit each main clade/species
nodeNumber <- ggtree(tree) + geom_text(aes(label=node), hjust=-.5, col = "blue", size = 1) # looks horrible but it gives the clade number

Sicydium_ML_tree <-suppressWarnings(suppressMessages(print(ggtree(tree, size = .4) + 
  xlim(-0.02, 0.26) +
  geom_treescale(x=0, y=-1.5, offset = -4) + 
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) > 80), size = 3, col= "black", vjust = -0.3, hjust=1.9, na.rm = FALSE) + 
  geom_nodepoint(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) > 70), size = 1, col= "black") + 
  geom_cladelabel(node=216, label="Sicydium plumieri", color="red", hjust = -0.07, fontsize = 3.5, offset = 0.002, fontface="italic") + 
  geom_cladelabel(node=108, label="Sicydium brevifile", color="blue", hjust = -0.01, vjust = 0.2, fontsize = 3.5, fontface="italic") + 
  geom_cladelabel(node=408, label="Sicydium salvini", color="purple", hjust = -0.07, fontsize = 3.5, offset = 0.002, fontface="italic") + 
  geom_cladelabel(node=356, label="Sicydium punctatum", color="brown", hjust = -0.07, fontsize = 3.5, offset = 0.002, fontface="italic") + 
  geom_cladelabel(node=320, label="Sicydium buscki", color="black", hjust = -0.07, fontsize = 3.5, offset = 0.002, fontface="italic") + 
  geom_cladelabel(node=407, label="Sicydium crenilabrum", color="orange", hjust = -0.03, vjust = 0.3, fontsize = 3.5, offset = 0.004, fontface="italic") +
  geom_cladelabel(node=211, label="Awaous spp.", color="darkgreen", hjust = -0.07, fontsize = 3.5, offset = 0.002, fontface="italic") +
  geom_hilight(node=336, fill="green") +
  #geom_hilight(node=332, fill="green") +
  geom_hilight(node=135, fill="green") +
  geom_hilight(node=121, fill="green") +
  geom_hilight(node=120, fill="green") +
  geom_hilight(node=139, fill="green") +
  theme(plot.margin = unit(c(0.5,0.5,0.5,0.5), "cm"))))) 


```




```{r demo-plot2, fig.cap="A plot of random numbers"}
plot(rnorm(10))
```

Figure \@ref(fig:demo-plot) shows how we can have a caption and cross-reference for a plot

```{r demo-inline-code}
x <- round(pi, 2)
```

Here is an example of inline code `r x` in the middle of a sentence. 

# Discussion

# Conclusion

Busck´s Stone-Biting Goby, *Sicydium buscki*, is a component of the fish fry “teti” fishery in Eastern Cuba. This species represents the only taxa of the orden Gobiiformes confirmed by molecular tools as part of such a fishery.
More thorough investigations and identification of the species comprising the “teti” fishery are needed. It is imperative to include them in  local management plans and to avoid overfishing this resource.

# Acknowledgements


<!-- The following line inserts a page break  -->

\newpage

# References 

<!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->

<div id="refs"></div>

\newpage

### Colophon

This report was generated on `r Sys.time()` using the following computational environment and dependencies: 

```{r colophon, cache = FALSE}
# which R packages and versions?
if ("devtools" %in% installed.packages()) devtools::session_info()
```

The current Git commit details are:

```{r}
# what commit is this file at? 
if ("git2r" %in% installed.packages() & git2r::in_repository(path = ".")) git2r::repository(here::here())  
```
